---
title: "eds223 test map"
author: "Marie Rivers"
date: "9/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(RColorBrewer)
library(rgeos)
library(sp)
library(rnaturalearth)
library(rnaturalearthdata)
library(sf)
library(spData)
# library(spDataLarge) # package ‘spDataLarge’ is not available for this version of R
library(tidyverse)
library(tmap)
```

Messages when loading library(rgeos):
Loading required package: sp
rgeos version: 0.5-8, (SVN revision 679)
 GEOS runtime version: 3.8.1-CAPI-1.13.3 
 Please note that rgeos will be retired by the end of 2023,
plan transition to sf functions using GEOS at your earliest convenience.
 Linking to sp version: 1.4-5 
 Polygon checking: TRUE

Message when trying to install package spDataLarge:
Warning in install.packages :
  package ‘spDataLarge’ is not available for this version of R

A version of this package for your version of R might be available elsewhere,
see the ideas at
https://cran.r-project.org/doc/manuals/r-patched/R-admin.html#Installing-packages

# Natural Earth Data
```{r}
sp::plot(ne_countries())
```
```{r}
# uk
plot(ne_countries(country = "united kingdom"))
```
```{r}
tm_shape(lnd) +
  tm_fill() +
  tm_borders()
```
```{r}
map_london = tm_shape(lnd) + tm_polygons()
map_london
```
```{r}
if (requireNamespace("rgdal", quietly = TRUE)) {
library(rgdal)
columbus <- readOGR(system.file("shapes/columbus.shp", package="spData")[1])
plot(columbus)
}
if (requireNamespace("spdep", quietly = TRUE)) {
library(spdep)
col.gal.nb <- read.gal(system.file("weights/columbus.gal", package="spData")[1])
}
```
```{r}

```

